%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{Introduction}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

In the era of Industry 4.0, companies use modern technology to optimize
traditional manufacturing and industrial processes. As human labor is expensive,
companies search for new ways to minimize human assistance. One of the senses
that could not be replaced easily for a long time is eyesight. However, with
recent advances in the field of \bld{computer vision}, some tasks can be done by
robots. The robots usually consist of camera systems that allow them to
perceive their surroundings and make decisions.

In 2015 scientists from Microsoft Research team proposed a \bld{deep learning}
model \cite{surp2015} that surpassed human-level accuracy on a visual
recognition task on the ImageNet 2012 classification dataset \cite{imagenet}.
Since then, even superior models were proposed \cite{resnet, efficientnet}.
These high-performing image recognition models became the basis of
state-of-the-art \bld{object detection} models which are the key component of
machine perception as their task is to localize the objects in the scene.

There are many areas in industry where machine perception is useful. For
instance, the models can be trained to detect faulty products soon enough to
take corrective actions to ensure the products' quality. It is also a vital part
of robotic arms that can carry out non-trivial tasks such as items picking,
sorting, and packing. Another example of use can be observed in autonomous
delivery navigation robots that can pick up trays of objects and move them
around in a larger area such as a warehouse or a car factory \cite{bmw}.

The main goal of the thesis is \bld{to research} and \bld{to summarize} some of
the state-of-the-art object detection methods based on deep learning approach.
The \bld{models are evaluated on various real-world datasets} provided by
collaborating company \bld{SANEZOO EUROPE}, which offers solutions to problems
such as AI robot guidance and 3D vision inspection of products. Different models
are compared using appropriate metrics for object detection tasks. The results
are then summarized and discussed. For future evaluations on arbitrary datasets,
\bld{we implement a benchmarking tool} that provides an interactive way to train
and evaluate models.

The thesis is divided into six chapters. We start by introducing the object
detection task and the evaluation metrics we use to measure the object detection
models' performance. Next, we define the key components of deep learning models.
After defining all relevant concepts, we describe the models we have
chosen for our evaluation. \myref{Chapter}{chap:evaluation} introduces the
provided datasets, describes the expected
results, training settings, and finally summarizes the evaluation outcomes.
\myref{Chapter}{chap:tool} describes the use case, the design, and the
implementation of our benchmarking tool. Lastly, we recapitulate our
contributions and propose future work in the final
\myref{Chapter}{chap:conclusion}. We use \bld{bold text} to highlight important
parts of text such as newly introduced terms, important concepts or explanations.

